On the presentation of orthogonal groups over polynomial rings

### 2019-01-08 dl-paper.tex
One more case covered

\begin{rem} Our goal is to rewrite $x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X))$, where $f_1(X) \in M[X]$, $f_2(X) \in A[X]$ as
 $g \cdot x_\alpha(\frac{aX^{-1}}{1+am}) \cdot \{ 1 + am, X \}$ for some $g \in G_+$
 and $m \in M$. At first assume that $\Phi$ is simply-laced. \end{rem}
\begin{enumerate}
 \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.} (Is this the same thing as $\alpha \perp \beta$?)
  Obviously, in this case $g = z_\beta(f_1(X), f_2(X))$, $m=0$.
 \begin{comment} 
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
 \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
 \end{comment}
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 Start from this formula (centrality of $K_2$-paper):
 \begin{multline}
 x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
 \end{multline}
 \item {\it Case $\beta - \alpha \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 \begin{multline}
  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1});
 \end{multline}
 \item {\it Case $\beta = -\alpha$, $f_1(X) = mX$, $f_2(X)=0$}. %CASE 1
For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
(except in the sole case when $\alpha$ is a long root of a symplectic root system).
Now direct computation using~\eqref{eq:dennis-stein} and centrality of symbols shows that:
\begin{multline}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
 = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
\end{multline}
 \item Essentially this allows one to cover the case $\beta = -\alpha$, $f_1(X) = Xm$ (with the same answer)
\end{enumerate}

>>>>

\begin{rem} Our goal is to rewrite $x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X))$, where $f_1(X) \in M[X]$, $f_2(X) \in A[X]$ as
 $g \cdot x_\alpha(\frac{aX^{-1}}{1+am}) \cdot \{ 1 + am, X \}$ for some $g \in G_+$
 and $m \in M$. At first assume that $\Phi$ is simply-laced. \end{rem}
\begin{enumerate}
 \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.} (Is this the same thing as $\alpha \perp \beta$?)
  Obviously, in this case $g = z_\beta(f_1(X), f_2(X))$, $m=0$.
 \begin{comment} 
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
 \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
 \end{comment}
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 Start from this formula (centrality of $K_2$-paper):
 \begin{multline}
 x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
 \end{multline}
 \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 \begin{multline}
  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1});
 \end{multline}
\item {\it Case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$}.
Suffices to prove the assertion under the assumption $f_2(X)=0$.
First consider the case $f_1(X) = mX$, where $m\in M$. For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
(except in the sole case when $\alpha$ is a long root of a symplectic root system).
Now direct computation using~\eqref{eq:dennis-stein} and centrality of symbols shows that:
\begin{multline}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
 = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
\end{multline}

Now suppose $f_1(X) = X^2f_1'(X)$. Choose $\gamma$ such that $\alpha + \gamma \in \Phi$.
Then everything we need follows from the computation:
\begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X^2 mf_1'(X)) \cdot x_\alpha(-aX^{-1}) = 
 {}^{x_\alpha(aX^{-1})}[x_{-\alpha - \gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)), x_{\gamma}(X)] = \\
 = [x_{-\alpha-\gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)) x_{-\gamma}(N_{-\alpha-\gamma, \gamma} N_{-\alpha-\gamma, \alpha} af_1'(X)), x_\gamma(X) x_{\alpha+\gamma}(N_{\alpha,\gamma}a)].
\end{multline*} 
\end{enumerate}
